---
title: "The app, and putting it on Posit Connect"
description: >
  RunApp() is the six charts as one Shiny app, on a study's own tables or on
  files a reader loads. How to run it, what a server needs to run it, what
  was measured, and what has not been tested.
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

`RunApp()` is the six bio.viz charts as one Shiny app. Shiny does two jobs in it and no more: it holds the tables, and its R session answers every statistic a chart asks for. The charts are the package's widgets, with the controls they already have.

## Run it

```{r}
library(gsm.bio)

RunApp()
```

With no table the app opens on the synthetic study that ships with the package. Give it a study's own tables and it opens on those:

```{r}
RunApp(dfResults, dfParticipants, dfOutcomes)
```

- The results table is the only one needed: one row per participant, biomarker and visit, with the columns `USUBJID`, `TEST`, `STRESN`, `VISIT` and `VISITNUM`.
- With a participants table (`USUBJID` and whatever describes a participant) the charts offer groups and filters. Without one they have none.
- With an outcomes table (`USUBJID`, `PARAMCD`, `PARAM`, `AVAL` and `CNSR`) the stratified survival chart is drawn. Without one its place holds a sentence saying so.

A table that lacks a column is refused with a sentence naming the column. `lSettings` opens a chart on a view of your choosing, under that chart's name and bio.viz's setting names:

```{r}
RunApp(
  dfResults, dfParticipants,
  lSettings = list(GroupComparison = list(start_value = "CRP", group_by = "ARM"))
)
```

## A reader's own files

The first pill in the app's header opens the Data page. It has a card for each table: results, which the charts need, and participants and outcomes, which are optional. A reader chooses a file in a card, each a `.csv`, `.xpt` or `.sas7bdat` file.

- R reads the file on the server. `.xpt` and `.sas7bdat` files are read with haven.
- The card shows the file's first rows as R read them, under the file's own column names. A number is written in full, not as `1e+05`.
- The card asks which column of the file is each one the charts need. A column that already has gsm.bio's name for it is filled in and tagged "same name". One the reader has still to say is amber and tagged "say which".
- A file R cannot read is reported in the card it was chosen in, with R's sentence.
- A file is taken away with the Remove control in its card. Until then it is one of the files the button draws, and the page names them all beside the button, so a file chosen for an earlier study is seen before it is drawn again.
- On the button the columns are renamed to gsm.bio's names and the charts are drawn on the reader's tables. The page then lists the charts that are ready, each with what it draws, and each opens from the list. A chart that lacks a table says which.
- Nothing is drawn on a table until every column is said. A column left unsaid, a column chosen twice, a result that is text and a file R cannot read are each answered with a sentence beside the button, and the charts stay as they were. An optional file R cannot read holds the button until it is removed or another is chosen.

A rail beside the cards, above them on a phone, counts what is left in three steps: the files chosen and any R could not read, the columns still to say, and the charts that are ready. Under the steps it says what the charts are drawn on now, which stays the tables they were on until the button is pressed.

Above the cards the Data page shows what is loaded: the tables the charts are drawn on, ten rows at a time, with where each came from. After the button it shows the reader's tables.

The file is held in the R session's memory and nowhere else. Nothing is written to the server beyond Shiny's own temporary copy of an upload, which goes when the session ends, and nothing is kept between sessions: a reader who comes back loads the file and says its columns again.

The app accepts files up to 100 MB. Shiny's own limit is 5 MB; `nMaxUploadMB` sets another.

## Where the statistics come from

Every statistic is computed on request by the R session behind the page, by gsm.bio's own `Analyze_*()` functions, and the line under a chart says so, naming the R and the gsm.bio of the server it runs on: for example, "computed by R 4.3.3 with gsm.bio 0.4.0 on this server". A saved widget page can answer only what was stored when it was made; the app answers every view its controls reach.

- The rows a chart draws are sent to the session with each request, because the chart works them out in the page: a change from baseline, the filters and the cuts are applied there, and R tests those rows and no others.
- The session runs the nine `Analyze_*()` functions and nothing else. Any other name a page sends is answered with a sentence and nothing is called. The rows and the arguments are read as data, never as R code.
- A number crosses to the page as JSON at sixteen significant digits, as a stored result's does.

## On Posit Connect

The deployment is one file. It ships with the package, at `system.file("app", "app.R", package = "gsm.bio")`:

```{r}
library(shiny)
library(haven)
library(gsm.bio)

RunApp()
```

The three packages are attached by name so that the record Connect installs the app from lists each of them. To open on a study's own tables, read them in that file and hand them to `RunApp()`; the file's own comments show how.

Put the file in a folder of its own and deploy the folder:

```{r}
dir.create("gsm-bio-app")
file.copy(system.file("app", "app.R", package = "gsm.bio"), "gsm-bio-app")

rsconnect::deployApp("gsm-bio-app", appName = "gsm-bio", appTitle = "Biomarker charts")
```

What the server needs:

- gsm.bio installed on your own machine from GitHub, with `remotes::install_github("jwildfire/gsm.bio@v0.4.0")` or pak. The tag names the release: without it the line installs the default branch, `dev`, which is the work in progress. rsconnect records where each package was installed from and refuses one it cannot trace to a source, so a copy loaded from a checkout with `devtools::load_all()` will not deploy.
- A route from the Connect server to GitHub, to install gsm.bio there, and to a CRAN repository for shiny, haven and the rest. gsm.bio is not on CRAN.
- A version of R on the server near the one you deploy from. R's own answers can differ between versions, which is why the line under each chart names the R that computed it.

Two settings on the content's Runtime tab are worth a look:

- Several readers share one R process by default, and R does one thing at a time: while it computes one reader's statistic, the others wait. Most statistics here take a few thousandths of a second (below). The known slow one is Fisher's exact test on a large table. If readers wait, lower "Max connections per process" so Connect starts more processes.
- A process that is idle is stopped after a while and the next reader waits for R to start. "Min processes" of 1 keeps one running.

## What was measured

On the synthetic study, 11,472 results rows for 200 participants and 12 biomarkers, with the browser and the server on one machine (R 4.3.3, an Apple laptop). The times were measured at gsm.bio 0.3.0.9000, commit c52f2c7, when the app was first whole, and not again at the release. A network adds its own time. `data-raw/app-timing.R` in the repository measures it again.

From choosing a chart to R's answer on the page, which includes sending the tables to the page and drawing the chart:

| Chart | Time | Largest message to the session |
|---|---|---|
| Association scatter | 0.25 s | 7 kB |
| Correlation matrix | 0.22 s | 18 kB |
| Biomarker screen | 0.25 s | 20 kB |
| Cross-tabulation | 0.19 s | 7 kB |
| Stratified survival | 0.23 s | 6 kB |

From choosing another test in the group comparison to its answer, with the chart already drawn: 16 to 18 thousandths of a second, in one message of 5 kB.

These are one run's times. Another run on the same machine differs by a few hundredths of a second for a chart and a few thousandths for a test.

No chart sends the whole results table with a request: it sends the rows it draws, which here is at most one row per participant with a column per biomarker. The table that grows with a study is the one sent to the page when a chart is opened, all of it, each time.

## What has not been tested

No one has deployed this app to a Posit Connect server yet. The sessions that built it had no server to deploy to. What stands in for that:

- The suite runs the app in a second R session and drives it in a headless browser: each chart is opened, a statistic no saved page stores is asked for and held to R's own answer, and a file of each of the three types is loaded and drawn.
- The record Connect installs from was written for real, once, by `data-raw/connect-manifest.R`: it installs gsm.bio from GitHub into a library of its own and runs `rsconnect::writeManifest()` on the deployment folder. What it printed is below.

```{r, echo = FALSE, eval = TRUE, comment = ""}
cat(readLines("app-manifest.txt"), sep = "\n")
```

The first real deployment is the check on the rest: whether the server can reach GitHub, how long R takes to start there, and how the app behaves with several readers. What it finds belongs in an issue on [gsm.bio](https://github.com/jwildfire/gsm.bio/issues).
